**

### 2010-05-11 BD_disc/paper.tex
updates - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2265 25464f21-6099-402c-b30a-640f1d40d38b

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\newcommand\mnras{MNRAS}
\newcommand\pasp {PASP}
\newcommand\aj   {AJ}
\newcommand\apj  {ApJ}
\newcommand\apjl  {ApJL}
\newcommand\apjs  {ApJS}
\newcommand\aap  {A\&A}
\newcommand\aaps  {A\&AS}
\newcommand\apss  {AP\&SS}
\newcommand\gca  {Geochim. Cosmochim. Acta}
\newcommand\araa {ARA\&A}
\usepackage{multirow}

@@

\begin{abstract}
SORT OUT REFERENCE TO THE FILTER RESPONSES IN THE SEDS FIGURES say
discussed later
more about stellar photosphere overlapping with disc

FINESSE FIGURE SIZES

CHANGE ALL WORDING FOR NEW FIGURES** CHANGED AGE TO 1 MYR FOR SUB
FIGURES AND NEED TO ACKNOWLEDGE THROUGHT

CHOSE 10 MYRS AS PRE-MS CONTRACTION AGES ARE PROBABLY A  FACTOR OF 2 WRONG

ADD FILTERS TO OTHER SEDS FIGURES

Note about fitting objects in the next paper.

   \end{abstract}

@@

Theoretical study of Brown Dwarfs (BDs) and the subsequent development
of testable hypotheses for observational studies is a critical, and
somewhat uncertain, area within the field of star and planet
formation. Several of the key physical parameters and mechanisms
remain unclear within this mass regime
\citep{2007ApJ...664.1154S}. Uncertainty remains over fundamental
issues such as the initial formation mechanisms, the subsequent
evolution and dominance of a star-disc interaction through to the
possible dependence of planet formation mechanisms on stellar mass
\citep[for a review of BD formation mechanisms see
][]{2006astro.ph..2367W}.

Perhaps the two most fundamental challenges are formulating the
formation mechanism of BDs and deriving the resulting
initial-mass-function (IMF). Whether the BD IMF or formation
mechanisms are different to their higher mass, solar-type, equivalents
(T Tauri Stars, hereafter termed TTS) is an open question. Derivations
of reliable IMFs depend, obviously, on robust derivations of stellar
mass, and more subtly, on derivations of stellar ages (as IMFs are
usually defined for assumed coeval populations). The study of
classical T Tauri (CTTS) and disc systems of
\cite{1997AJ....114..288M} found that given an expected range of
parameters the scatter in infrared photometry matched the observed
CTTS locus well. However the work of \cite{1997AJ....114..288M},
discussed in more detail later, only included parameterised `flat'
discs. Once disc flaring is considerd it is clear from previous work
that misidentification of high mass stars with circumstellar discs is
likely. \cite{2004ApJ...617.1177W} show that high-mass (HM) stars with
circumstellar discs are likely to be mis-identified as younger Class I
sources. This problem also exists at lower masses where the presence
of circumstellar discs can dramatically shift the spectral energy
distributions (SEDs) and therefore colours and magnitudes of BDs
\citep{2004MNRAS.351..607W}. Therefore, deriving robust masses (and
ages), and subsequently IMFs for BDs requires an understanding of
these effects of disc presence.

@@

Some studies of disc lifetimes find no significant difference between
BD stars and their higher mass counterparts
\citep{2003AJ....126.1515J}, however a possible correlation of disc
lifetime with stellar mass is proposed in \cite{2007ApJ...660.1517S}.
Additionally, \cite{2009arXiv0901.2603K} find that, for TTS older than
3 Myrs, the disc dispersal time is mass dependent for intermediate
mass (IM) to solar-type stars. This result only holds for the mass
transition stated (IM to solar-type) and is based on stars with
combined dust signatures, from infrared (IR) excesses and accretion
indicators (using a EW[H$\alpha$], criterion).
\cite{2009arXiv0901.4120D} also find, for TTS, a mass dependent
general SED shape for disc candidates, with higher mass stars showing
a featureless continuum at $\lambda>$8.0$\mu$m with lower mass stars
generally showing strong silicate and PAH features at 10 and 2$\mu$m,
indicative of mass dependent disc evolution. Whether in fact the disc
lifetimes and therefore rate or type of involved physical processes
are a function of stellar mass could provide another piece of evidence
separating the previously assumed continuous (in mass) evolutionary
principles of stars into a dichotomy separated by the hydrogen-burning
mass limit, and alter the probability of forming planets in the BD
regime.

@@

Several mechanisms may act to completely dissipate a circumsteller
disc. These include accretion from the disc ($\delta M_{\rm
  disc}=\dot{M}$), photoevaporation or photoionisation due to flux
from the central and neighbouring stars, and the formation of giant
planets or interaction with binary partners. However, the entire disc
does not have to be dissipated to be missed by disc fraction surveys.
More subtly, disc fractions can be altered due to wavelength dependent
detection. This is due to the peak flux of the thermal blackbody
emission of the disc being proportional to the temperature,
$\lambda^{\rm thermal}_{\rm peak}\propto T_{\rm disc}$, and the
temperature in the disc being approximately a function of distance
from the star. Thus for a given system, as one increases the
wavelength of observation, the corresponding radial position of the
effective source will increase. Moreover, as the disc flux must be
separated from the photospheric flux the important quantity is the
separation in wavelength between the emission peaks for the stellar
and thermal disc components. Therefore the presence of an inner disc
hole can change derived disc fractions, as a function of
wavelength. Interestingly, \cite{2009arXiv0901.2603K} find that
results for disc dissipation timescales based only on their accretion
indicators or inferred disc presence do not agree, perhaps due to
inclusion of transitional objects, where the inner disc is being
cleared, and is therefore not detected at their target
wavelength. \cite{2009arXiv0901.2603K} suggest that this is caused by
photoevaporation of the inner disc, leading to a mass dependent disc
lifetime, at their wavelength, for their sample. However, as discussed
in \cite{2009arXiv0901.4120D}, the inner hole can be created via dust
grain growth and midplane settling, giant planet formation or
photoevaporation by ultraviolet (UV) and far-UV (FUV) flux
\citep{2007MNRAS.378..369N}.  \cite{2009arXiv0901.4120D} argue that if
binarity or giant planet formation or photoevaporation cause inner
disc clearing the resulting system would not show active accretion
from radii below the inner disc boundary. For the case of clearing by
dust grain growth and settling accretion from a hot gas disc within
the inner radius is still possible, and indeed evidence for such a hot
gas inner disc has been found through SED fitting
\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Additionally,
\cite{2009arXiv0901.4445E} argue that for M stars, with a pure
reprocessing disc where the inner disc radius ($R_{\rm inner}$) is
equal to the dust sublimation radius ($R_{\rm dust}$, discussed in
Section \ref{physics}), the stellar and thermal components are not
separable at wavelengths shorter than 6$\mu$m. In the case of
\cite{2009arXiv0901.4445E}, the inner disc hole was created by
photoionising radiation from the central star destroying the dust
component of the disc. Recent direct evidence for a photoevaporating
disc has been found for the circumstellar disc around a low mass TTS
in the Sigma Orionis cluster \citep{2009arXiv0902.0457R}. The
detection was characterised by a tenuous photoevaporation wind and
little or no accretion, and a disc detection at 24$\mu$m indicative of
a large inner hole. Additionally, for BDs, \cite{2009arXiv0902.0638M}
find that the disc mass and radius distributions in the Orion
Trapezium cluster are consistent with photoevaporation over 1 Myr (the
adopted age of the cluster), from UV and FUV flux generated by the
massive $\theta^1$ Ori C.

@@

Although the creation of the inner disc hole could have several
causes, at least part of the effect is undoubtedly due to
accretion. Accretion acts to directly deplete the inner disc (where
the material is accreted from). Accretion also depletes the inner disc
indirectly, as accretion generates hot continuum emission
\citep{1998ASPC..154.1709G}, increasing the photoionising UV and FUV
flux available \citep{1998ASPC..154.1709G}, and therefore affecting
the derived disc fraction \citep{2009arXiv0901.3684H}. This effect may
be amplified for BDD systems where the combined photospheric emission
is dominated by accretion flux. However, accretion columns modeled by
\cite{2004MNRAS.348..879A} were found to produce negligible levels of
photoionising flux due in part to the high optical depth of the column
itself to Lyman continuum photons. Additionally, due to the high
concentrations of hydrogen in the accretion column and hotspot the
emission is more likely to be characterised by a stellar atmosphere
than a black body. However, for our work as emission from a stellar
atmosphere or a black body of equal temperature are approximately
equal for wavelengths longer than the Lyman edge we have neglected
this effect. Whilst the accretion column and hotspot may not
contribute to the photoinising flux within the system they will of
course alter the disc evolution by an increase of the emitted
flux. This increase in flux will lead to an increase in temperature of
the disc inner and outer regions, and more particulary a change in the
dust sublimation effects at the inner edge.

The current proposed mechanism of accretion is a magnetically
channelled accretion `column', where material from a truncated (at the
co-rotation radius $R_{\rm co}$) inner disc boundary falls onto the
surface of the star along magnetic field lines
\citep{1990RvMA....3..234C,1991ApJ...370L..39K}. This mechanism is
widely accepted, with strong evidence found from the excessive widths
of H$\alpha$ ($>$10$\AA$) emission lines, over that caused by
chromospheric activity and stellar rotation
\citep{1998ASPC..154.1793W}, caused by the high velocities of
infalling matter, ~100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.

Accretion rates can be derived by modelling this magnetospheric
accretion with a characteristic `column' temperature and assuming
statistical equilibrium of the state populations. The resulting line
ratios can then be fitted to the observed spectra. Accretion rates can
also be calculated from model comparison of the Equivalent Width (EW)
of the H$\alpha$ line itself, or perhaps more reliably, as they are
less affected by extinction, that of the hydrogen recombination lines
of Pa$\beta$ and Br$\gamma$. Accretion rates have been derived using
these methods for many TTS and more recently for BDs
\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
with accretion rates in the range $\dot{M_{\rm
    acc}}=$10$^{-6}$-10$^{-12} M_{\odot}yr^{-1}$, and typical
accretion rates in the range log$(\frac{\dot{M}}{M_{\odot}}
yr^{-1})=$-10 to -8 with only FU Orionis type objects accreting at
rates higher than this. The mechanism producing accretion rates as
high as those observed episodically in FU Orionis type objects is
likely to be produced by some accretion mechanism instability, or
perhaps by encounters with other cluster members \citep[see][for
discussion]{2008arXiv0810.2854P}. Additionally, much lower accretion
rates of $\dot{M}\approx$ 10$^{-13}M_{\odot}yr^{-1}$ have been derived
for BDs using flux blueward of 4000$\AA$ where the photospheric flux
becomes negligible \citep{2009arXiv0901.3684H}.

@@

If disc-locking is present for BDD systems, as for TTS stars, one
would expect accretion of material from a magnetic truncation radius,
$R_{\rm T}$ \citep{2007prpl.conf..479B}.  \cite{2007prpl.conf..479B}
show that the magnetic truncation radius, $R_{\rm T}$, must be less
than the co-rotation radius, $R_{\rm co}$ (where the Keplerian angular
rotation rate of the disc is the same as the angular rotation rate of
the star), as material outside this radius will have too much angular
momentum to fall onto the star. This is implicitly adopted in the
proposed accretion mechanism, where the disc is magnetically
truncated, and therefore locked to the star. This magnetic truncation
would lead to an inner wall (and inner hole) of the accretion
disc. Evidence for an inner disc wall has been found from near-IR
excesses from the inner rims of Herbig Ae stars, with emission peaking
at 2-3$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
position of this wall is affected by several factors, discussed
further in Sections \ref{dust_edge} and \ref{inner_edge}. The previous
work of \cite{1997AJ....114..288M} explored the effects of simple mass
accretion and the radius to the inner disc on the infrared colours of
CTTS, useing a prescribed range of inner disc
radii. \cite{1997AJ....114..288M} find that the scatter in infrared
colours for there parameter range, $R_{\rm inner}=$1$-$12$R_*$ and
$\dot{M_{\rm acc}}=$10$^{-9}$to 10$^{-5} M_{\odot}yr^{-1}$, matches
the scatter of the CTTS locus found in the data. The models of
\cite{1997AJ....114..288M} used physically flat discs however meaning
their results will not stand for discs with significant flaring. More
importantly for our work \cite{1997AJ....114..288M} find a correlation
of the infrared locus of models with the accretion and inner disc
location. Essentially, changes in the stellar flux levels and position
of the inner wall lead to temperature changes of this inner edge and
therefore changes in the balance of flux across the infrared
wavelength regime. As this study does not include the effects of
vertical hydrostatic equilibirum or even the study of flared discs one
would expect, perhaps, a more complex relationship between the inner
edge position and infrared excess in `real' systems. This means that
studies aiming to provide evidence of disc locking by comparing disc
indicators with rotation rates may include unforseen biases. As the
rotation rate will effect the co-rotation radius and therefore
truncate the disc at different radii, thereby enhancing or suppressing
any relationship of infrared excess (or disc presence) with rotation
rate.

In summary, several key areas in the theoretical studies of BDs hinge
critically on observational constraints, where the derived values are
heavily affected by disc and/or accretion presence.  Formation
mechanisms, IMFs, disc dissipation timescales, accretion rate--stellar
mass relationships and studies of disc-locking mechanisms using
correlations of rotation rates with infrared excesses, all require
derivations of either masses, ages or disc fractions (or a
combination), supplemented by other parameters. The consequences of
the disc structure for BD accretion discs, particularly vertical
structure, given the assumption of vertical hydrostatic equilibrium,
have already been discussed for a limited range of BD parameters in
\cite{2004MNRAS.351..607W}. Indeed \cite{2004MNRAS.351..607W} have
shown that BDD systems seen at higher inclinations can be confused
with CTTS systems, having similar colours and
magnitudes. Additionally, a benchmark model grid of spectra for star
and disc systems in the mass range 0.1$M_{\odot}<M_*<$50$M_{\odot}$
has previously been published in \cite{2006ApJS..167..256R}.

@@

The structure of this paper is as follows. In Section \ref{model} we
outline the model used, including an explanation of our physical
assumptions (Section \ref{physics}), a brief description of the
radiative transfer code (Section \ref{torus}), and an explanation of
the derivation of emergent quantities such as photometric magnitudes
(Section \ref{derived}). The ranges of the input variables are then
explained and, where possible, justified using observational
constraints in Section \ref{par_space}, with the total parameter space
covered shown in Table \ref{par_space_table}. Section
\ref{disc_struct} then contains analysis and description of the
resulting temperature and dust density structures of the discs. The
consequences of these changes in disc structure on the SEDs of these
objects is then discussed in Section \ref{sed_analysis}. Section
\ref{photometry} then details problems caused for the derivation of
the primary parameters age, mass and disc fractions from photometry
and the resulting relations built on these parameters; accretion rate
to stellar mass and rotational period to disc presence. Finally,
conclusions are drawn, with a summary, in Section
\ref{conclusions}.**REWRITE AT END**A CASE STUDY IS THEN INCLUDED AS
SECTION \ref{object}.**

@@

To model an accreting BDD system we must first model the underlying
photospheric flux. To provide a self-consistent set of model spectra
we have adopted a BD stellar interior and atmospheric model grid. We
have then constructed the total photospheric flux for any input value
of stellar age and mass by interpolating for surface gravity (log(g)),
effective temperature ($T_{\rm eff}$), radius ($R_*/R_{\odot}$) and
luminosity ($L_*/L_{\odot}$). These values were then used to
interpolate atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2}
\AA^{-1}$) from 1200 to 2$\times$ 10$^7$ $\AA$ (or 0.12 to 2000
$\mu$m). These spectra were then smoothed using 200 logarithmically
spaced points. Careful inspection ensured that no spectral features
were removed during smoothing. The stellar interior models used for
this study are the `DUSTY00' models of \cite{2000ApJ...542..464C}
combined with the `AMES-Dusty', atmospheric models of
\cite{2000ApJ...542..464C}, which are all available online
\footnote{http://perso.ens-lyon.fr/france.allard/}. For our
approximate $T_{\rm eff}$ (effective temperature) range of $\approx
$3000K$<T_{\rm eff}<$1600K the AMES-Dusty atmospheres are most
applicable (2700K$>T_{\rm eff}>$1700K). We did try including dynamic
application of atmospheres based on the derived $T_{\rm eff}$,
i.e. using AMES-Cond for $T_{\rm eff}<$1700K, however this resulted in
large discontinuities between the model atmospheres and resulting
spectra. As this only affects stars at the very edge of our
temperature range, i.e. for the oldest and lowest mass objects (for
the AMES-Cond case), we have adopted the same model throughout.

@@

Secondly, we require a model of the accretion flux for the system. The
flux due to accretion was added onto the intrinsic photospheric flux
using the simple approximation of blackbody emission. The selected
accretion rate was used to derive an accretion luminosity ($L_{\rm acc}$),
where the material was modelled as falling from the disc inner edge
onto the surface of the star. $L_{\rm acc}$ is calculated according to
\ref{Lacc}, 
\begin{equation}
{L_{\rm acc}=\frac{GM_*\dot{M}}{R_*}\times (1-\frac{R_*}{R_{\rm inner}})},
\label{Lacc}
\end{equation}
where $M_*$ is the stellar mass, $\dot{M}$ the mass accretion rate,
$R_*$ the stellar radius and $R_{\rm inner}$ the radius of the disc inner
boundary.

>>>>

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\newcommand\mnras{MNRAS}
\newcommand\pasp {PASP}
\newcommand\aj   {AJ}
\newcommand\apj  {ApJ}
\newcommand\apjl  {ApJL}
\newcommand\apjs  {ApJS}
\newcommand\aap  {A\&A}
\newcommand\aaps  {A\&AS}
\newcommand\apss  {AP\&SS}
\newcommand\gca  {Geochim. Cosmochim. Acta}
\newcommand\araa {ARA\&A}
\newcommand\logmdot {$\log \dot{M}$}
\usepackage{multirow}

@@

\begin{abstract}
To Do
\begin{enumerate}
\item{Read new papers and put in any relevant stuff.}
\item{Sort structure paragraph at end of intro.}
\item{Sort out headings of sections.}
\item{Sort clearpage problem, perhaps change to includegraphics.}
\item{Sort out the webpage stuff.}
\end{enumerate}
\end{abstract}

@@

Theoretical study of Brown Dwarfs (BDs) and the subsequent development
of testable hypotheses for observational studies is a critical, and
somewhat uncertain, area within the field of star and planet
formation. Several of the key physical parameters and mechanisms
remain unclear within this mass regime \citep{2007ApJ...664.1154S}.
Uncertainty remains over fundamental issues such as the initial
formation mechanisms, the subsequent evolution and dominance of a
star-disc interaction through to the possible dependence of planet
formation mechanisms on stellar mass \citep[for a review of BD
formation mechanisms see][]{2006astro.ph..2367W}.

Perhaps the two most fundamental challenges are formulating the
formation mechanism of BDs and deriving the resulting
initial-mass-function (IMF). Whether the BD IMF or formation
mechanisms are different to their higher mass, solar-type, equivalents
(T Tauri Stars, hereafter termed TTS) is an open question. Derivations
of reliable IMFs depend, obviously, on robust derivations of stellar
mass, and more subtly, on derivations of stellar ages (as IMFs are
usually defined for assumed coeval populations). The study of
classical T Tauri (CTTS) and disc systems of
\cite{1997AJ....114..288M} found that given an expected range of
parameters the scatter in infrared photometry matched the observed
CTTS locus well. However the work of \cite{1997AJ....114..288M},
discussed in more detail later, only included parametrised `flat'
discs. Once disc flaring is considered it is clear from previous work
that misidentification of high mass stars with circumstellar discs is
likely. \cite{2004ApJ...617.1177W} show that high-mass (HM) stars with
circumstellar discs are likely to be mis-identified as younger Class I
sources. This problem also exists at lower masses where the presence
of circumstellar discs can dramatically shift the spectral energy
distributions (SEDs) and therefore colours and magnitudes of BDs
\citep{2004MNRAS.351..607W}. Therefore, deriving robust masses (and
ages), and subsequently IMFs for BDs requires an understanding of
these effects of disc presence.

@@

Some studies of disc lifetimes find no significant difference between
BD stars and their higher mass counterparts
\citep{2003AJ....126.1515J}, however a possible correlation of disc
lifetime with stellar mass is proposed in \cite{2007ApJ...660.1517S}.
Additionally, \cite{2009arXiv0901.2603K} find that, for TTS older than
3 Myrs, the disc dispersal time is mass dependent for intermediate
mass (IM) to solar-type stars. This result only holds for the mass
transition stated (IM to solar-type) and is based on stars with
combined dust signatures, from infrared (IR) excesses and accretion
indicators (using a EW[H$\alpha$], criterion).
\cite{2009arXiv0901.4120D} also find, for TTS, a mass dependent
general SED shape for disc candidates, with higher mass stars showing
a featureless continuum at $\lambda>8.0$\,$\mu$m and lower mass stars
generally showing strong silicate and PAH features at 10 and 2\,$\mu$m,
indicative of mass dependent disc evolution. If the disc lifetimes and
therefore rate or type of involved physical processes are a function
of stellar mass. This could provide another piece of evidence
separating the previously assumed continuous (in mass) evolutionary
principles of stars. Resulting in a dichotomy separated by the
hydrogen-burning mass limit. This would also lead to a change in the
probability of forming planets in the BD regime, compared to CTTS.

@@

Several mechanisms may act to completely dissipate a circumsteller
disc. These include accretion from the disc ($\delta M_{\rm
  disc}=\dot{M}$), photoevaporation or photoionisation due to flux
from the central and neighbouring stars, and the formation of giant
planets or interaction with binary partners. However, the entire disc
does not have to be dissipated to be missed by disc fraction surveys.
More subtly, disc fractions can be altered due to wavelength dependent
detection. This is due to the peak flux of the thermal blackbody
emission of the disc being proportional to the temperature,
$\lambda^{\rm thermal}_{\rm peak}\propto T_{\rm disc}$, and the
temperature in the disc being approximately a function of distance
from the star. Thus for a given system, as one increases the
wavelength of observation, the corresponding radial position of the
effective source will increase. Moreover, as the disc flux must be
separated from the photospheric flux the important quantity is the
separation in wavelength between the emission peaks for the stellar
and thermal disc components. Therefore the presence of an inner disc
hole can change derived disc fractions, as a function of
wavelength. Interestingly, \cite{2009arXiv0901.2603K} find that
results for disc dissipation timescales based only on their accretion
indicators or inferred disc presence do not agree, perhaps due to
inclusion of transitional objects, where the inner disc is being
cleared, and is therefore not detected at their target
wavelength. \cite{2009arXiv0901.2603K} suggest that this is caused by
photoevaporation of the inner disc, leading to a mass dependent disc
lifetime, at their wavelength, for their sample. However, as discussed
in \cite{2009arXiv0901.4120D}, the inner hole can be created via dust
grain growth and mid plane settling, giant planet formation or
photoevaporation by ultraviolet (UV) and far-UV (FUV) flux
\citep{2007MNRAS.378..369N}.  \cite{2009arXiv0901.4120D} argue that if
binarity or giant planet formation or photoevaporation cause inner
disc clearing the resulting system would not show active accretion
from radii below the inner disc boundary. For the case of clearing by
dust grain growth and settling accretion from a hot gas disc within
the inner radius is still possible, and indeed evidence for such a hot
gas inner disc has been found through SED fitting
\citep{2005ApJ...623..952E,2008ApJ...689..513T}. Additionally,
\cite{2009arXiv0901.4445E} argue that for M stars, with a pure
reprocessing disc where the inner disc radius ($R_{\rm inner}$) is
equal to the dust sublimation radius ($R_{\rm dust}$, discussed in
Section \ref{physics}), the stellar and thermal components are not
separable at wavelengths shorter than 6\,$\mu$m. In the case of
\cite{2009arXiv0901.4445E}, the inner disc hole was created by
photoionising radiation from the central star destroying the dust
component of the disc. Recent direct evidence for a photoevaporating
disc has been found for the circumstellar disc around a low mass TTS
in the Sigma Orionis cluster \citep{2009arXiv0902.0457R}. The
detection was characterised by a tenuous photoevaporation wind and
little or no accretion, and a disc detection at 24\,$\mu$m indicative of
a large inner hole. Additionally, for BDs, \cite{2009arXiv0902.0638M}
find that the disc mass and radius distributions in the Orion
Trapezium cluster are consistent with photoevaporation over 1 Myr (the
adopted age of the cluster), from UV and FUV flux generated by the
massive $\theta^1$ Ori C.

@@

Although the creation of the inner disc hole could have several
causes, at least part of the effect is undoubtedly due to
accretion. Accretion acts to directly deplete the inner disc (where
the material is accreted from). Accretion also depletes the inner disc
indirectly, as accretion generates hot continuum emission
\citep{1998ASPC..154.1709G}, increasing the photoionising UV and FUV
flux available \citep{1998ASPC..154.1709G}, and therefore affecting
the derived disc fraction \citep{2009arXiv0901.3684H}. This effect may
be amplified for BDD systems where the combined photospheric emission
is dominated by accretion flux. However, accretion columns modeled by
\cite{2004MNRAS.348..879A} were found to produce negligible levels of
photoionising flux due in part to the high optical depth of the column
itself to Lyman continuum photons. Additionally, due to the high
concentrations of hydrogen in the accretion column and hotspot the
emission is more likely to be characterised by a stellar atmosphere
than a black body. However, for our work as emission from a stellar
atmosphere or a black body of equal temperature are approximately
equal for wavelengths longer than the Lyman edge we have neglected
this effect. Whilst the accretion column and hotspot may not
contribute to the photoinising flux within the system they will of
course alter the disc evolution by an increase of the emitted
flux. This increase in flux will lead to an increase in temperature of
the disc inner and outer regions, and more particularly a change in the
dust sublimation effects at the inner edge.

The current proposed mechanism of accretion is a magnetically
channelled accretion `column', where material from a truncated (at the
co-rotation radius $R_{\rm co}$) inner disc boundary falls onto the
surface of the star along magnetic field lines
\citep{1990RvMA....3..234C,1991ApJ...370L..39K}. This mechanism is
widely accepted, with strong evidence found from the excessive widths
of H$\alpha$ ($>$10\,\AA) emission lines, over that caused by
chromospheric activity and stellar rotation
\citep{1998ASPC..154.1793W}, caused by the high velocities of
infalling matter, $~$100-200 kms$^{-1}$ \citep{1998ApJ...492..743M}.

Accretion rates can be derived by modelling this magnetospheric
accretion with a characteristic `column' temperature and assuming
statistical equilibrium of the state populations. The resulting line
ratios can then be fitted to the observed spectra. Accretion rates can
also be calculated from model comparison of the Equivalent Width (EW)
of the H$\alpha$ line itself, or perhaps more reliably, as they are
less affected by extinction, that of the hydrogen recombination lines
of Pa$\beta$ and Br$\gamma$. Accretion rates have been derived using
these methods for many TTS and more recently for BDs
\citep{2003ApJ...592..266M,2004A&A...424..603N,2006A&A...452..245N},
with accretion rates in the range $\dot{M}_{\rm
    acc}=$10$^{-6}$--10$^{-12} M_{\odot}yr^{-1}$, and typical
accretion rates in the range \logmdot = log$(\frac{\dot{M}}{M_{\odot}}
yr^{-1})=-10$ to $-8$ with only FU Orionis type objects accreting at
rates higher than this. The mechanism producing accretion rates as
high as those observed episodically in FU Orionis type objects is
likely to be produced by some accretion mechanism instability, or
perhaps by encounters with other cluster members \citep[see][for
discussion]{2008arXiv0810.2854P}. Additionally, much lower accretion
rates of $\dot{M}\approx$ 10$^{-13}M_{\odot}yr^{-1}$ have been derived
for BDs using flux blueward of 4000\,\AA where the photospheric flux
becomes negligible \citep{2009arXiv0901.3684H}.

@@

If disc-locking is present for BDD systems, as for TTS stars, one
would expect accretion of material from a magnetic truncation radius,
$R_{\rm T}$ \citep{2007prpl.conf..479B}. \cite{2007prpl.conf..479B}
show that the magnetic truncation radius, $R_{\rm T}$, must be less
than the co-rotation radius, $R_{\rm co}$ (where the Keplerian angular
rotation rate of the disc is the same as the angular rotation rate of
the star), as material outside this radius will have too much angular
momentum to fall onto the star. This is implicitly adopted in the
proposed accretion mechanism, where the disc is magnetically
truncated, and therefore locked to the star. This magnetic truncation
would lead to an inner wall (and inner hole) of the accretion disc.
Evidence for an inner disc wall has been found from near-IR excesses
from the inner rims of Herbig Ae stars, with emission peaking at
2--3\,$\mu$m \citep{2001ApJ...560..957D}. The actual shape and radial
position of this wall is affected by several factors, discussed
further in Sections \ref{dust_edge} and \ref{inner_edge}. The previous
work of \cite{1997AJ....114..288M} explored the effects of simple mass
accretion and the radius to the inner disc on the infrared colours of
CTTS, using a prescribed range of inner disc radii.
\cite{1997AJ....114..288M} find that the scatter in infrared colours
for there parameter range, $R_{\rm inner}=$1$-$12$R_*$ and
$\dot{M_{\rm acc}}=$10$^{-9}$to 10$^{-5} M_{\odot}yr^{-1}$, matches
the scatter of the CTTS locus found in the data. The models of
\cite{1997AJ....114..288M} used physically flat discs however meaning
their results will not stand for discs with significant flaring. More
importantly for our work \cite{1997AJ....114..288M} find a correlation
of the infrared locus of models with the accretion and inner disc
location. Essentially, changes in the stellar flux levels and position
of the inner wall lead to temperature changes of this inner edge and
therefore changes in the balance of flux across the infrared
wavelength regime. As this study does not include the effects of
vertical hydrostatic equilibrium or even the study of flared discs one
would expect, perhaps, a more complex relationship between the inner
edge position and infrared excess in `real' systems. This means that
studies aiming to provide evidence of disc locking by comparing disc
indicators with rotation rates may include unforeseen biases. As the
rotation rate will effect the co-rotation radius and therefore
truncate the disc at different radii, thereby enhancing or suppressing
any relationship of infrared excess (or disc presence) with rotation
rate.

In summary, several key areas in the theoretical studies of BDs hinge
critically on observational constraints, where the derived values are
heavily affected by disc and/or accretion presence. Formation
mechanisms, planet formation, IMFs, disc dissipation timescales,
accretion rate--stellar mass relationships and studies of disc-locking
mechanisms using correlations of rotation rates with infrared
excesses, all require derivations of either masses, ages or disc
fractions (or a combination), supplemented by other parameters. The
consequences of the disc structure for BD accretion discs,
particularly vertical structure, given the assumption of vertical
hydrostatic equilibrium, have already been discussed for a limited
range of BD parameters in \cite{2004MNRAS.351..607W}. Indeed
\cite{2004MNRAS.351..607W} have shown that BDD systems seen at higher
inclinations can be confused with CTTS systems, having similar colours
and magnitudes. A benchmark model grid of spectra for star and disc
systems in the mass range 0.1$M_{\odot}<M_*<$50$M_{\odot}$ has
previously been published in \cite{2006ApJS..167..256R}.

@@

**THIS PARAGRAPH IS CURRENTLY WRONG, WILL REQRITE AT THE END**

The structure of this paper is as follows. In Section \ref{model} we
outline the model used, including an explanation of our physical
assumptions (Section \ref{physics}), a brief description of the
radiative transfer code (Section \ref{torus}), and an explanation of
the derivation of emergent quantities such as photometric magnitudes
(Section \ref{derived}). The ranges of the input variables are then
explained and, where possible, justified using observational
constraints in Section \ref{par_space}, with the total parameter space
covered shown in Table \ref{par_space_table}. Section
\ref{disc_struct} then contains analysis and description of the
resulting temperature and dust density structures of the discs. The
consequences of these changes in disc structure on the SEDs of these
objects is then discussed in Section \ref{sed_analysis}. Section
\ref{photometry} then details problems caused for the derivation of
the primary parameters age, mass and disc fractions from photometry
and the resulting relations built on these parameters; accretion rate
to stellar mass and rotational period to disc presence. Finally,
conclusions are drawn, with a summary, in Section \ref{conclusions}..

@@

To model an accreting BDD system we must first model the underlying
photospheric flux. To provide a self-consistent set of model spectra
we have adopted a BD stellar interior and atmospheric model grid. We
have then constructed the total photospheric flux for any input value
of stellar age and mass by interpolating for surface gravity (log(g)),
effective temperature ($T_{\rm eff}$), radius ($R_*/R_{\odot}$) and
luminosity ($L_*/L_{\odot}$). These values were then used to
interpolate atmospheric spectra for flux (ergs s$^{-1}$cm$^{-2}
{\rm \AA}^{-1}$) from 1200 to 2$\times$ 10$^7$ \AA (or 0.12 to 2000\,
$\mu$m). These spectra were then smoothed using 200 logarithmically
spaced points. Careful inspection ensured that no spectral features
were removed during smoothing. The stellar interior models used for
this study are the `DUSTY00' models of \cite{2000ApJ...542..464C}
combined with the `AMES-Dusty', atmospheric models of
\cite{2000ApJ...542..464C}, which are all available online
\footnote{http://perso.ens-lyon.fr/france.allard/}. For our
approximate $T_{\rm eff}$ (effective temperature) range of $\approx
$3000\,K$<T_{\rm eff}<$1600\,K the AMES-Dusty atmospheres are most
applicable (2700\,K$>T_{\rm eff}>$1700\,K). We did try including dynamic
application of atmospheres based on the derived $T_{\rm eff}$,
i.e. using AMES-Cond for $T_{\rm eff}<$1700\,K, however this resulted in
large discontinuities between the model atmospheres and resulting
spectra. As this only affects stars at the very edge of our
temperature range, i.e. for the oldest and lowest mass objects (for
the AMES-Cond case), we have adopted the same model throughout.

@@

Secondly, we require a model of the accretion flux for the system. The
flux due to accretion was added onto the intrinsic photospheric flux
using the simple approximation of blackbody emission. The selected
accretion rate was used to derive an accretion luminosity ($L_{\rm acc}$),
where the material was modelled as falling from the disc inner edge
onto the surface of the star. $L_{\rm acc}$ is calculated according to
\ref{Lacc}, 
\begin{equation}
{L_{\rm acc}=\frac{GM_*\dot{M}}{R_*} \left( 1-\frac{R_*}{R_{\rm inner}}\right)},
\label{Lacc}
\end{equation}
where $M_*$ is the stellar mass, $\dot{M}$ the mass accretion rate,
$R_*$ the stellar radius and $R_{\rm inner}$ the radius of the disc inner
boundary.

The initial inner disc radius was set to be the co-rotation radius
(this is discussed in more detail in Section
\ref{disc_parameters}). During the radiative transfer simulations of
the disc the final inner dust disc radius may be extended past the
co-rotation radius. This is due to dust sublimation effects (see
Sections \ref{dust_edge} and \ref{inner_edge} for an
explanation). However, as the gas within the disc is not sublimated it
will always extend down to the co-rotation radius and we assume
accretion will still occur from this radius. A full discussion of the
differences between the initial and resulting final radii of the dust
disc can be found in Section \ref{inner_edge}. Once the accretion
luminosity was derived, an adopted areal coverage ($A$), over the
stellar surface, was used to calculate an effective temperature
($T_{\rm acc}$), for the accretion `hot' spot, where
\begin{equation}
{T_{\rm acc}=\left(\frac{L_{\rm acc}}{4\pi R^2_{*} \sigma A}\right)^{\frac{1}{4}}}.
\label{Tacc}
\end{equation}
